\providecommand{\main}{../..}
\documentclass[\main/dresen_thesis.tex]{subfiles}
  \renewcommand{\thisPath}{\main/chapters/monolayers}

\begin{document}
  \chapter{Monolayer}\label{ch:monolayers}
    For nanocubes the arrangement of highest order in the plane is the square lattice.
    In the following, the preparation of such self-assembled lattices with long-range order is presented.
    First, the synthesis and characterization of magnetic nanocubes is described, which are subsequently used to produce the monolayer samples.
    All parameters that have to be considered are discussed and rule of thumbs to estimate their optimal value are explained, such that the method can also be transferred to other batches of nanoparticles.
    For selected monolayers, the quantitative evaluation of the structures is shown, as well as the characterization of their magnetic properties. Emergent magnetic properties that are not observed for the individual nanoparticles are described and compared to model calculations.

    \section{Cobalt Ferrite Nanocubes}
      \subfile{\thisPath/nanoparticles/nanoparticles}

    \section{Preparation of Monolayers}
      In the next step, the preparation of long-range ordered monolayers from a nanocube dispersion via drop-casting is described.
      Drop-casting is a material efficient and cheap method to prepare thin films.
      Experimental experience shows that the homogeneity of such samples suffers due to wetting effects during evaporation.
      The general approach to improve the quality achieved by drop casting is the usage of co-solvents.
      Therefore, a method to prepare monolayers of oleic acid coated nanoparticles of approx. $10 - 20 \unit{nm}$ size by drop-casting with co-solvents is discussed in the following.
      The basic idea is to use a mixture of a fast-evaporating solvent, such as n-heptane, as primary dispersion medium and a slow-evaporating solvent, such as 1-octadecene, as addend.
      After complete evaporation of the fast-evaporating component, a gentle heating step is performed to remove the remaining dispersion medium.
      The various parameters during drop-casting are discussed and optimal value estimation are presented to achieve high-quality monolayers with long range order.

      \subsection{Nanoparticle Concentration}
        The optimal concentration of the nanoparticles in dispersion for a monolayer on a given wafer surface area can be roughly estimated geometrically from the average particle to particle distance on the square lattice $a_{p-p}$.
        Assuming a perfect square lattice expanding over the wafer area $A_{\textsf{wafer}}$, the number of nanocubes is determined by
        \begin{align}
          N \eq \frac{A_{\textsf{wafer}}}{a_{p-p}^2}.
        \end{align}
        When the volume of a dispersion $V_{\textsf{disp.}}$ is dropped on the wafer, the number of particles in the drop is given by
        \begin{align}
          N \eq \frac{c_V V_{\textsf{disp}}}{V_p},
        \end{align}
        where $c_V$ is the particle volume concentration of the dispersion and $V_p$ the volume of a single nanocube.
        The average nanoparticle volume is known from the small-angle scattering model, and the particle volume concentration can be estimated by
        \begin{align}
          c_V \eq \frac{c_m}{\rho},
        \end{align}
        using the the particle mass concentration $c_m$ of the dispersion that is estimated from gravimetry, or more exact from a thermogravimetric analysis, and the density $\rho$ of the particle that can be estimated using the literature value.
        Combining these equations, the particle mass concentration of the dispersion needs to be tuned to the value
        \begin{align}\label{eq:monolayers:preparation:particleConcentration}
          c_m \eq \rho \frac{A_{\textsf{wafer}}}{V_{\textsf{disp}}} \frac{V_p}{a_{p-p}^2}
        \end{align}
        Typically, for ferrite nanocubes with the size in the order of $10 \unit{nm}$ with an oleic acid shell in the order of $2 \unit{nm}$, the optimal mass concentration for a drop of $50 \unit{\text{\textmu} L}$ on a $10\times 10 \unit{mm^2}$ wafer is in the order of $0.1 \unit{mg/mL}$.
        Using this calculated estimate, the optimal particle concentration can be determined for a batch of nanoparticles by a short experimental drop casting series around this value.
        In the case of a non-square lattices, the \refeq{eq:monolayers:preparation:particleConcentration} has to account for the reduced coverage by including an additional factor for the packing density $\eta$ in the plane and $a_{p-p}^2$ has to be replaced by the average maximum cross-section the particle is taking in the lattice.
        For a perfect circle packing, which is expected for densely packed spheres in two dimensions, the packing density is straight forward to evaluate to $\eta \eq \pi \sqrt{3} / 6 \approx 0.9069$.

      \subsection{Solvent Properties}
        \subfile{\thisPath/solventProperties/solventProperties}
        

      \subsection{Drying Conditions}
        The droplet of dispersion and solvents can be dried under varied conditions.
        The heating temperature...

    \section{Magnetic Structure}

    \section{Emergent Effects}

    \section{Model}

\end{document}