\providecommand{\main}{../../..}
\documentclass[\main/dresen_thesis.tex]{subfiles}

\begin{document}
  In this chapter the first systematic study on the preparation and properties of magnetic nanocube double layers is presented.
  Using the knowledge acquired from the monolayers chapter, single layers of nanocubes in square arrays are prepared on a silicon substrate, coated with a PMMA layer of tuneable thickness and finished with a second layer of nanocubes.

  The successful and reproducible preparation by this method is shown by SEM, XRR and NR, where the total sample thickness is directly correlated to the amount of PMMA spin coated between the double layer sandwich.
  The presence of the two nanocube layers is visible in the SEM cross-sectional micrographs, as well as by the correlation peak at $1 \unit{nm^{-1}}$ visible in both XRR and NR.

  The magnetism of double layered structures has been tackled by two approaches.
  First, the macroscopic magnetization of five samples with varied interlayer distance are studied by vibrating sample magnetometry.
  Correcting for slight differences in the sample observed at room temperature, which originate from the variation in measured sample area and small variations inherited from the drop-casting procedure, low-temperature field-dependent and temperature-dependent magnetization measurements are performed and directly compared to one another.
  From the temperature-dependent magnetization, the magnetic behaviour that is also observed for monolayers is closely reproduced in each case and no significant effects of interlayer coupling are visible.
  The low-temperature hysteresis measurements show no modification of the coercivity but a small variation in the magnitude of the magnetization jump around $\pm 100 \unit{mT}$.

  With polarized neutron reflectometry the magnetic structure of the samples is approached with depth-resolution to gain a better view of the relative magnetization direction in the two respective layers.
  By simulating double layer structures on basis of the monolayer SLD profile, the expectation for the magnetic splitting from a parallel and antiparallel direction are discussed.
  The most striking difference is observed in whether the peaks in the Kiessig fringes are separated in the case of a parallel alignment or touching in the case of an antiparallel alignment.
  This is transferred to qualitatively discuss the polarized neutron reflectivities of four double layer samples at saturation and at a negative field of $-100 \unit{mT}$ below the jump in the hysteresis.
  In each case a clear separation of the Kiessig fringes is observed and therefore a majorly parallel alignment of the two layers is concluded.
  \\

  Thus, by those two studies no strong signatures for an antiferromagnetic dipolar interlayer coupling could be observed.
  Instead from theoretical calculations and the experimental observations, the considered interlayer distances are large enough to consider the magnetic properties of the double layers closely to that of independent monolayers.
\end{document}