\providecommand{\main}{../../..}
\documentclass[\main/dresen_thesis.tex]{subfiles}

\begin{document}
  The preparation procedure for monolayers in the last chapter naturally sparks the idea to add additional layers on top of readily prepared monolayers to achieve samples of separated single nanoparticle layers.
  Layering of the monolayers allow to enhance the signal from properties of the two-dimensional system by increasing the magnetic volume and hope is that new properties arise from interlayer interactions.
  Despite the simplicity of this approach and many studies on monolayer samples, a thorough literature research was not able to yield a systematic study on double layers of nanoparticles, where this has been attempted.
  Possible reasons are as previous monolayer preparation approaches were limited in either producing reproducible homogeneous monolayers as incomplete second layers remain visible \cite{Mishra_2015_Polar, Bodnarchuk_2010_Large} or monolayers with methods such as Langmuir-Schaefer \cite{Ukleev_2017_Polar} are unpractical for the layer-by-layer deposition.
  \\

  The interaction of magnetic layers with non-magnetic spacers is studied in literature for layered systems prepared by molecular-beam epitaxy.
  A famous system hereof is the Fe/Cr/Fe sandwich structure studied by Binasch and Gr\"unberg \etal \cite{Binasch_1989_Enhan}, where $12 \unit{nm}$ thick iron layers are separated by a non-magnetic chromium layer in the order of  $1 \unit{nm}$.
  In such systems, the Nobel prize winning giant magneto-resistance was discovered, where the electrical resistance depends on whether the magnetizations in the two adjacent magnetic layers are parallel or antiparallel.
  And it was found that the coupling between the iron layers oscillates between ferromagnetic and anti-ferromagnetic as a function of the distance between the layers due to the complex nature of the interlayer exchange coupling \cite{Demokritov_1998_Biqua}.
  % The interlayer exchange coupling between the two ferromagnetic layers with magnetization $\vec{m}_1$, $\vec{m}_2$ that are separated by a non-magnetic spacer is phenomenologically given by \cite{Demokritov_1998_Biqua}
  % \begin{align}
  %   E_\mathrm{IEC} \eq -J_1 \vec{m}_1 \cdot \vec{m}_2 - J_2 (\vec{m}_1 \cdot \vec{m}_2)^2.
  % \end{align}
  % This included ferromagnetic coupling of the layers ($J_1 > 0$), antiferromagnetic coupling ($J_1 <0$) and higher order effects by the biquadratic exchange coupling $J_2$.
  % Nonetheless, the study shows how a simple double layer system could open the door to previously unknown physical effects.

  To study systematically double layers of long-range ordered nanocubes, samples are prepared by sequentially performing the drop casting procedure and the interlayer distance is controlled by adding non-magnetic PMMA as spacer material of varied thickness in between.
  Doing this, a study comparing the magnetization for such double layered nanostructures is performed with respect to the varied interlayer distance and any changes in the magnetic properties can be attributed to the interlayer interaction.

  As naturally interlayer distances are several $\unit{nm}$ thick by the oleic acid surfactant of the nanoparticles, it should not be expected to observe interlayer exchange coupling between nanoparticle double layers such as in the thin layer systems of Fe/Cr/Fe.
  But still it is possible that the layers interact via dipolar coupling.
  For an in-plane magnetization, dipolar interlayer coupling prefers the antiparallel alignment between two homogeneously magnetized layers with a non-magnetic spacer \cite{Labrune_2002_Dipol}.
  Due to the complex square array arrangement of the nanocubes, however, more complex and therefore richer ground states are conceivable, for which however no theoretical study could be found in literature yet.

  
                                                    
  % Studying the dipolar interaction of magnetic nanoparticles quantitatively requires in an experiment the knowledge of the single-particle properties, the relative distance of the particles and their relative orientation.
  % In the previous chapter of monolayers it was presented how the distance of the particles and their relative orientation are set by the self-assembled formation of a long-range ordered square lattice that enables the discussion of the interaction.
  % To take the discussion further, it is interesting to study how such an ordered collection of nanoparticles in a monolayer interact with another monolayer.
  % A natural idea is therefore to extend the two-dimensional layer structure into the third dimension by adding a second layer on top.

\end{document}