\providecommand{\main}{../../..}
\documentclass[\main/dresen_thesis.tex]{subfiles}
  \renewcommand{\thisPath}{\main/chapters/looselyPackedNS/summary}

\begin{document}
  In this first chapter, two batches of iron oxide nanospheres, as well as spin-coated layers and bilayer stacks of said nanospheres are characterized structurally and magnetically.
  Seeing that the nanospheres themselves have magnetic properties that deviate strongly from the bulk properties expected from any common iron oxide phase, such as magnetite, maghemite or w\"ustite, the first step is crucial.
  Without, it is impossible to evaluate whether magnetic properties observed in packed nanostructures are a result of the interparticle interaction or a result of the nanoparticle properties themselves.
  \\

  For the batch of larger nanospheres, IOS-11, a core-shell structure of w\"ustite-magnetite is observed by complimentary small-angle scattering and X-ray diffraction experiments, which have their results confirmed by electron microscopy and vibrating sample magnetometry.

  The spin-coated layer shows laterally short-range order and vertically a structure of layered nanospheres.
  Using GISAXS and reflectometry in combination with the results obtained from the nanoparticle characterization, it is shown that the sample can be structurally described by layers of nanospheres with overlapping oleic acid shells.
  Magnetically the layer has an enlarged blocking temperature in comparison to the non-interacting nanospheres in dispersion.
  Furthermore, the spontaneous magnetization and magnetic moment of the nanospheres in the layer are slightly enhanced.
  The enhanced blocking temperature can be interpret as a typical signature of dipolar interaction in the sample, but due to the complex core-shell nanosphere structure it is also possible to consider that further oxidation of the w\"ustite core has progressed in comparison to the nanospheres in dispersion and the observed enhanced properties are a result thereof.
  As a byproduct of this study, it was observed that the nanosphere layer compresses strongly upon cooling, which as observable effect has not yet been found in literature.

  The bilayer stacks from IOS-11 show qualitatively a similar magnetic behavior in polarized neutron reflectometry as the single layer.
  No peculiar effects are observed in the magnetic splitting of the Bragg peaks in the remanent states after zero-field cooling nor field cooling, and no significant signal is observed in the spin-flip channel.
  Neither for the sample with large non-magnetic PMMA spacing between the nanospheres layers, nor for the reduced spacer thickness.
  It can be deduced that if dipolar interlayer interaction is present in the samples, it is a weak effect that can not be observed by a qualitative discussion.
  For a quantitative layer-by-layer evaluation of the magnetization, the samples have proven as being too complex to discuss due to the large number of unknown parameters.
  Considering the metastable oxidation state of the nanospheres, it would in the end always remain the questions whether observed quantitative differences are due to a further oxidation progression or from a interparticle interaction.
  \\

  For the batch of smaller sized nanospheres IOS-7, small angle scattering suggests a pure phased state of magnetic nanoparticles, but a bimodal size distribution.
  The same discussion as for IOS-11 has been performed, where the structure and magnetism of the non-interacting nanoparticles in dispersion is determined.
  The spin-coated layer shows a low density packing from GISAXS and reflectometry. And magnetically a close agreement in blocking temperature with the nanospheres in dispersion is observed.
  On one hand, a $20 \%$ increase in magnetic moment is seen for the spin coated layer in comparison to the nanospheres from vibrating sample magnetometry, but no strong magnetic splitting is observed in polarized neutron reflectometry on the other hand.
  The bilayer stacks provide a similar story as observed for the samples discussed from IOS-11.
  \\

  Overall the considered system proves to show only subtle differences in the packed structures in direct comparison to the nanospheres in dispersion.
  To gain a better understanding from the study of dipolar interaction it crystallizes therefore that a much simpler sample structure is necessary.
  To achieve a better basis for discussion, the obtained results motivate the study on the preparation of thin layers of nanoparticles with a much higher degree of in-plane order.
  The results for the preparation of pure phased nanoparticles and long-range ordered monolayers thereof are presented in the following chapter.

\end{document}