\providecommand{\main}{../../..}
\documentclass[\main/dresen_thesis.tex]{subfiles}
\begin{document}
	\section*{Acknowledgements}
	\addcontentsline{toc}{chapter}{Acknowledgements}
	At this point I would like to reflect and thank everybody who has contributed in some way to the completion of this thesis.
	At first I'd like to speak a large thank you to my supervisor Sabrina Disch for the warm welcome to the group, letting me work on this interesting topic, supporting it financially, her continuous advice to further progress and for personally advancing me.
	Furthermore gratitude is spoken to Prof. Sanjay Mathur for being the co-supervisor of this thesis and his support.
	Prof. Uwe Ruschewitz is thanked for being the head of commission and Dr. Stefan Roitsch for being the secretary of the defense.

	Furthermore, the working group is thanked for their support at the institute and lively discussions on the topics: Dominika Zàkutnà, Maria Hentschel, Flore Mees and Yannic Falke.
	The latter two are furthermore acknowledged for their additional works done that contributed to this thesis during the performance of their Master and Bachelor's thesis respectively.

	Students that performed lab courses with me and have thereby produced results that are included in this thesis are greatly acknowledged: Christian Tobeck, Markus Kr\"uger, Rajitha Ravithas and Anne Hansen.

	The collaboration from the University of Mainz is thanked for providing samples and data for the chapter of the loosely-packed nanospheres: Wolfgang Tremel, Eugen Schechtel und Kristina Wichmann.

	A great acknowledgement is spoken to Viktor Klippert and everybody of his workshop for their dedicated support and ingenious talent to build anything that can be drawn on a piece of paper.

	The VCI is gratefully acknowledged for the financial support through the Kekulé grant.

	Annette Schmidt is thanked for sharing laboratory spaces and access to equipment to perform chemical work, Patricia Bach for everything that she does to keep the laboratories running.

	The colleagues Ahmad Shaaban, Matthias Kundt and Johanna Nothacker are gracefully acknowledged for sharing the journey.

	The instrumental scientists that have shown great support in data acquisition are acknowledged for their dedicated work:
	Emmanuel Kentzinger \& Michael Smik (GALAXI), Alexei Vorobiev \& Gunnar Pálsson \& Anton Devishvili (SuperADAM), Dirk Honecker (D22 \& D33), Stefan Mattauch \& Alexandros Koutsioumpas (MARIA), Thomas Saerbeck (D17) and Daniel Hermida Merino (BM26B)

	Ruth Bruker is thanked for being a support if problems at the scanning electron microscope occurred and for giving the introduction to the instrument.

	Andreas Mettenb\"orger is thanked for performing XRD measurements in the working group of Prof.\ Mathur.

	Stefan Roitsch additionally for performing the transmission electron microscopy measurements.

	The colleagues Marc Effertz, Julian Seifert, Yeimy Martinez, Melissa Hess, Eric Roeben, Alexey Bushmelev, Sascha Sprott, Daniel Stadler and Kevin Graef are thanked for the good times and the discussions during lunch.

	At last I'd like to thank Almut for always being there for me and providing me with mental and emotional support at all stages of this work with the patience of an angel.
\end{document}