\providecommand{\main}{../../../..}
\documentclass[\main/dresen_thesis.tex]{subfiles}

\begin{document}
  \paragraphNewLine{Transmission Electron Microscopy}
    The iron oxide nanocubes are investigated by transmission electron microscopy using a Zeiss Leo 902 (\refsec{ch:instruments:laboratoryInstruments:tem}).
    The micrographs were obtained at an acceleration voltage of $120 \unit{kV}$ with a \ch{LaB6} cathode in bright field mode.
    The nanocube edge length is determined from the micrographs by using the Fiji distribution \cite{Schindelin_2012_Fijia} to count 200 nanocube edges, which are binned in a histogram and evaluated by fitting a log-normal distribution as described in \refsec{ch:methods:em}.

  \paragraphNewLine{X-Ray Diffraction}
    An X-ray diffraction experiment of Ol-Fe-C was performed in cooperation with the group of Daniel Nižňanský from the Department of Inorganic Chemistry at the Charles University in Prague on an PANanalytical X'Pert PRO, described in \refsec{ch:instruments:laboratoryInstruments:xrd}.
    For the measurement the sample was transported in a dry state to the University in Prague, where it was redispersed and subsequently transferred on a glass substrate for measurement.
    The diffractometer is equipped with a Cu-K$\alpha$ source ($\lambda \eq 1.54 \angstrom$) and a $2 \theta \eq 5^\circ \ldots 80^\circ$ has been measured.
    The instrumental resolution is determined from a \ch{LaB6} reference measurement (SR 660b, NIST).

    The nanocubes XRD data are evaluated by a LeBail fit using the FullProf suite \cite{Rodriguez_1993_Recen} as described in \refsec{ch:methods:xrd}.
    The background is estimated manually by selecting 20 background points, from which the background in the measured range is interpolated linearly.
    The data between $5 ^\circ \ldots 15 ^\circ$ is excluded from the refinement due to a strong background coming from the glass substrate in this range.
    As in the previous chapters that discuss nanoparticles synthesized from oleates, two phases are necessary to describe the XRD.
    The experimental data is therefore refined to a combination of an inverse spinell phase (space group $Fd\bar{3}m$, No. 227) and a w\"ustite phase (space group $Fm\bar{3}m$, No. 225).

  \paragraphNewLine{Small-Angle Scattering}
    The nanoparticle structure of Ol-Fe-C is studied in dispersion using both small-angle X-ray and neutron scattering.
    The SAXS measurement was performed at GALAXI (\refsec{ch:lss:galaxi}), where the nanoparticles were dispersed in toluene and filled in borosilicate capillaries (Hilgenberg) with $1.5 \unit{mm}$ diameter and a $0.01 \unit{mm}$ wall thickness.
    A plastic stopper and a glue gun were used to seal the capillaries for the measurement in vacuum.
    The samples have been measured on the largest ($3.53 \unit{m}$) and shortest ($0.83 \unit{m}$) sample-to-detector distances possible at GALAXI at the Ga-K$\alpha$ wavelength of $\lambda \eq 1.3414 \unit{\angstrom}$.
    For the background subtraction, a capillary filled with toluene and an empty capillary is measured and the data is scaled to absolute units following the protocol described in \refsec{ch:methods:saxs}.

    For SANS and SANSPOL, the D33 instrument (\refsec{ch:lss:d33}) has been utilized.
    The nanocubes were dried over night at ambient conditions, and then redispersed in toluene-$\mathit{d_8}$ by sonification to minimize the hydrogen content in the sample.
    For the measurement, the dispersions are filled in Hellma quartz cuvettes with a thickness of $2 \unit{mm}$.
    The velocity selector at D33 was set to a wavelength of $6 \unit{\angstrom}$, with a wavelength spread of $10 \%$ (FWHM).
    The sample was measured both at a sample-to-detector distance of $11 \unit{m}$ and $2 \unit{m}$ to cover a large $q$-range.
    The collimation-to-sample distance were $10.3 \unit{m}$ and $5.3 \unit{m}$ respectively.
    With the collimation aperture of $30 \times 30 \unit{mm^2}$ and the sample aperture of $7 \times 10 \unit{mm^2}$, the angular instrumental resolution parameters are estimated to $\Delta \theta_\mathrm{11 m} \eq 1.60 \unit{mrad}$ and $\Delta \theta_\mathrm{2 m} \eq 3.79 \unit{mrad}$ respectively according to \refeq{eq:methods:sans:instrumentalResolution}.
    The Ol-CoFe-C dispersion was measured at ambient conditions without the application of a magnetic field at $6 \unit{mT}$ guide field, as well as at a magnetic field of $1.234 \unit{T}$. % $153 \unit{mT}$, $308 \unit{mT}$, $600 \unit{mT}$, $882 \unit{mT}$, and
    The magnetic field is applied by an electromagnet perpendicular to the beam in the horizontal plane.
    The data is reduced using the GRASP software \cite{Dewhurst_2003_Grasp}, where the solvent is subtracted and the data is corrected for the polarization efficiency of $99 \%$ and the flipping efficiency of $97 \%$.
    The azimuthal average of the magnetic scattering is obtained from a $20 ^\circ$ sector around the vertical $z$ direction, whereas the nuclear scattering is obtained from averaging the complete detector area from the measurement at zero field.
    \\

    For the evaluation of the form factors from the azimuthally averaged small-angle scattering data, the same procedure as described in \refsec{sec:looselyPackedNS:characterization:nanoparticles} for iron oxide nanospheres is performed using a superball core-shell form factor instead of a spherical core-shell form factor.
    The superball form factor is described in detail in \refsec{sec:monolayers:methods:superballFF}.
    For the nanoparticle core a composition of \ch{FeO} is assumed and for the shell an inverse spinell structure of \ch{Fe_{3-$\delta$} O4}, where the composition and lattice constants as estimated from X-ray diffraction are used to determine and fix the scattering length densities.
    The solvent scattering length density of toluene and toluene-\textit{d8}, as well as oleic acid for X-rays and neutrons are used as given in \refsec{sec:monolayers:nanoparticle:structuralCharacterization}.

    The total particle size and particle size distribution is determined by the fit of the SAXS data and fixed to the same value for the SANS fit.
    The angular resolution parameters in the SANS fit are freely varied to allow for a deviation from the given estimate.
    The core/shell fraction of the particle is, however freely fit in both fits as it cannot be excluded that the nanocubes oxidized in between the experiments.
    The surfactant shell is ignored in the SAXS fit due to the poor contrast between oleic acid and toluene.
    For SANS there is however a strong contrast between oleic acid and the solvent and therefore the surfactant shell thickness is considered here.

  \paragraphNewLine{Vibrating Sample Magnetometry}
    To measure the room temperature magnetic properties of the nanocubes, a ADE EV 7 Vibrating Sample Magnetometer is used.
    For the measurement an empty Teflon pot is first measured to determine the background susceptibility and subsequently, $20 \unit{\musf L}$ of the stock solution Ol-Fe-C, which contain approximately $0.75 \unit{mg}$ of nanocubes is dried in the pot.
    The dry sample is then measured in a range of $\pm 2 \unit{T}$ at ambient conditions ($295 \unit{K}$).
    From the obtained data, the empty pot measurement is subtracted and a sum of two Langevin behaviour with excess susceptibility is fit to the data
    \begin{align}
      \begin{split}
        &M(H) \eq \tilde{M}_{s,\,1} \mathcal{L}( \mu_1 \mu_0 H / k_B T) + \tilde{M}_{s,\,2}  \mathcal{L}(  \mu_2 \mu_0 H / k_B T) + \tilde{\chi} \mu_0H,\\
        \mathrm{with\,} & \hspace{0.2cm} \mathcal{L}(x) \eq \coth(x) - 1/x,
      \end{split}
    \end{align}
    to determine the spontaneous magnetizations $\tilde{M}_{s,\,i}$ in units of $\unit{memu}$ and the magnetic moments $\mu_i$, as well as the excess susceptibility $\tilde{\chi}$.
    
    The spontaneous magnetizations in units of $\unit{memu}$ correspond, as described in \refsec{ch:methods:vsm}, to a sum over the number of individual magnetic moments $\tilde{M}_{s,\,i} \eq N_i \mu_i$.
    Thus the number of moments in the two modes is determined by the ratio $N_i \eq \tilde{M}_{s,\,i} / \mu_i$.

    To scale the measured magnetization to the magnetic volume and thus to units $\unit{kA \, m^{-1}}$, the volume of the magnetic material in the sample needs to be estimated.
    In \refsec{ch:methods:vsm} the case of a single mode is described, where the magnetic volume is determined by $N V_p$, where $N$ is the number of magnetic moments obtained from the Langevin fit and $V_p$ is the size of a nanoparticles determined from SAS.
    In the present case, this is not so straight forward due to a core-shell structure of the nanoparticles.
    Estimating $N \eq N_1 + N_2$ and considering for each moment a volume of $V_p$ overestimates the volume of the magnetic material as instead of a core-shell structure the full particle volume is considered for each moment $\mu_1$ and $\mu_2$ respectively.
    A more reasonable estimate is given by setting $N \eq N_1$ for the consideration of the magnetic volume.
    This corresponds to stating that each moment in the primary mode $\mu_1$ corresponds to a nanoparticle and the secondary mode is phenomenologically included in these nanoparticles.
    Then the total magnetic volume is given by $V_\mathrm{mag} \eq N_1 V_p$, where $V_p$ is determined from SAS.
    % Additionally, the nanocubes that were forcibly oxidized are measured in VSM by the same procedure.
    % Here, the nanocube sample has a mass of approximately $0.17 \unit{mg}$.
\end{document}